Applying Renormalization Group Theory to the Square Well Liquid

### 2014-05-23 papers/thesis-roth/project.tex
Project writing Tested on elliot. Took 0:19.69.

% vector
\newcommand{\rr}{\ensuremath{\bf{r}}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

Where $\fattr$ is the contribution due to the longest-wavelenght density fluctuations. At this stage, I do not entirely understand why Forte splits up $\fattr$.

@@

@@

\subsubsection{Ideal gas}\label{sub2sec:ID}
The ideal gas term is purely local \fixme{whatever that means}:
\begin{align}
  \fid &= n\kT\left(\log(n) - 1\right)
\end{align}

\subsubsection{Hard sphere repulsion}\label{sub2sec:HS}
Hard sphere repulsive forces are dealt with by the White Bear version of Fundamental-Mearuse Theory.\cite{Roth02} The hard sphere excess free energy is given in the homogeneous case as
\begin{align}
  \fhs &= \kT\left( \Phi_1(n) + \Phi_2(n) + \Phi_3(n) \right)
\end{align}
The $\Phi_j(n)$ terms are given as
\begin{align}
  \Phi_1(n) &= -n_0\ln(1 - n_3) \\
  \Phi_2(n) &= \frac{n_1n_2}{1 - n_3} \\
  \Phi_3(n) &= n_2^3\left( \frac{n_3 + (1 - n_3)^2\ln(1 - n_3)}{36\pi n_3^2(1 - n_3)^2} \right)
\end{align}
The \emph{fundamental measure densities} are
\begin{align}
  n_0(n) &= \frac{n_2}{4\pi R^2} \nonumber \\
  &= n \\
  n_1(n) &= \frac{n_2}{4\pi R} \nonumber \\
  &= nR \\
  n_2(n) &= n4\pi R^2 \\
  n_3(n) &= n\frac{4}{3}\pi R^3 \nonumber \\
  &= \eta
\end{align}
where $\eta$ is the packing fraction.

@@

We use the isothermal compressibility in terms of packing fraction $\eta$, given by the Percus-Yevick exprssion:\cite{Barker76}
\begin{align}
  K^\text{HS} &= \frac{\left(1 - \eta\right)^4}{1 + 4\eta + 4\eta^2}
\end{align}

\fixme{And introduction to TPT---why do we use it?}
This discussion follows primarily from \textit{Theory of Simple Liquids}, by Hansen and McDonald\cite{Hansen06}.

The pair potential $v(\1,\2)$ describes the interaction between two hard spheres. For the square-well model, the pair potential is
\begin{align}
  v_\text{SW}(\1,\2) &=
    \begin{cases}
      \infty & r < \sigma \\
      -\epsilon & \sigma < r < \lambda\sigma \\
      0 & \lambda\sigma < r
    \end{cases}
\end{align}
For this work I use $\lambda = 1.5$.

Now, consider this to be the reference, and add a small perturbation:
\begin{align}
  v_\lambda(\1,\2) &= v_\text{SW}(\1,\2) + \lambda w(\1,\2) \label{eqn:small-perturbation}
\end{align}

The total potential energy of our system is
\begin{align}
  V_N(\lambda) = \sum_{i=1}^N\sum_{j>i}^N v_\lambda(\mathbf{r}_i,\mathbf{r}_j)
\end{align}

Given the \emph{configuration integral} (the potenial energy component of the partition function)
\begin{align}
  Z_N &= \int d\mathbf{r}^N\, e^{-\beta V_N}
\end{align}
and the non-ideal part of the free energy (i.e.~the excess free energy) is
\begin{align}
  F &= -\kT\ln\left( \frac{Z_N}{V^N} \right)
\end{align}
where $V^N$ is the total volume \fixme{I think?}, then the derivative of the excess free energy with respect to the coupling parameter $\lambda$ is
\begin{align}
  \frac{\partial F}{\partial\lambda} &= -\kT\left( \frac{1}{Z_N}\frac{\partial Z_N}{\partial\lambda} \right) \\
  &= -\kT\frac{1}{Z_N}\int d\mathbf{r}^N\, e^{-\beta V_N}(-\beta)\frac{\partial V_N}{\partial\lambda} \\
  \hookrightarrow \beta\frac{\partial F}{\partial\lambda} &= \beta\left\langle V_N^{'}(\lambda) \right\rangle_\lambda \\
  \hookrightarrow \beta F &= \beta F_0 + \beta\int_0^1 d\lambda\, \left\langle V_N^{'}(\lambda) \right\rangle_\lambda
\end{align}
where $\left\langle V_N^{'}(\lambda) \right\rangle_\lambda$ is the canonical ensemble average. We can take a series expansion of this average:
\begin{align}\begin{split} % too long; use split environment, and align to a space (&{})
  \left\langle V_N^{'}(\lambda) \right\rangle_\lambda = &{} \left\langle V_N^{'}(\lambda)\right\rangle_{\lambda = 0} + (\lambda)\frac{\partial}{\partial\lambda}\left\langle V_N^{'}(\lambda) \right\rangle_{\lambda}\bigg|_{\lambda = 0} \\ &{} + \mathcal{O}(\lambda^2)
\end{split}\end{align}
The derivative term is
\begin{align}
  \frac{\partial}{\partial\lambda}\left\langle V_N^{'}(\lambda) \right\rangle_{\lambda} &= \left\langle V_N^{''} \right\rangle_\lambda - \beta\sigma_\lambda^2
\end{align}
where
\begin{align}
  \sigma_\lambda^2 &\equiv \left\langle \left[ V_N^{'}(\lambda) \right]^2 \right\rangle_\lambda - \left\langle V_N^{'}(\lambda) \right\rangle^2_\lambda
\end{align}
\fixme{I don't really understand how this derivative is \ldots derived}
Putting this together, we have
\begin{align}
  \begin{split}
    \beta F = &{} \beta F_0 + \beta(1 - 0)\left\langle V_N^{'}(\lambda) \right\rangle_{\lambda = 0} \\ &{} - \beta\frac{1}{2}(1 - 0)^2\left(\left\langle V_N^{''}(\lambda = 0) \right\rangle_{\lambda = 0} - \beta^2\sigma^2_{\lambda = 0} \right)
  \end{split} \\
  \begin{split}
    =&{}  \beta F_0 + \beta\left\langle V_N^{'}(\lambda) \right\rangle_{\lambda = 0} \\ &{} - \beta\frac{1}{2}\left(\left\langle V_N^{''}(\lambda = 0) \right\rangle_{\lambda = 0} - \beta^2\sigma^2_{\lambda = 0} \right) \label{eqn:complicated-HTE}
  \end{split}
\end{align}
Now, we can define the total perturbation energy as
\begin{align}
  W_N &= \sum_{i=1}^N\sum_{j>i}^N w_\lambda(\mathbf{r}_i,\mathbf{r}_j)
\end{align}
Then, following from equation~\ref{eqn:small-perturbation},
\begin{align}
  V_N^{'} &= \frac{\partial}{\partial\lambda}\left(\sum_{i=1}^N\sum_{j>i}^N \lambda w(\mathbf{r}_i,\mathbf{r}_j)\right) \nonumber \\
  &= W_N \\
  \therefore V_N^{''} &= 0
\end{align}
With this in mind, we can simplify equation~\ref{eqn:complicated-HTE} to the \emph{high-temperature expansion}, first derived by Zwanzig:\cite{Zwanzig54}
\begin{align}
  \begin{split}
    \beta F = &{} \beta F_0 + \beta\left\langle W_N \right\rangle_0  \\ &{} - \frac{1}{2}\beta^2\left( \left\langle W_N^2 \right\rangle_0 - \left\langle W_N \right\rangle_0^2 \right) + \mathcal{O}(\beta^3)
  \end{split}
\end{align}
Zwanzig further showed that the $n^{th}$ term could be written in terms of the mean fluctuations $\left\langle \left[ W_N - \left\langle W_N\right\rangle_0 \right]^\nu \right\rangle_0$ with $\nu \leq n$.

Writing the statistical averages in terms of the pair density $n_\lambda^{(2)}(\1,\2)$ (i.e. the probability of having a sphere at \1 and \2 \fixme{make this more clear?}) gives us
\begin{align}
  \frac{\beta F}{N} &= \frac{\beta F_0}{N} + \frac{\beta}{2N}\int_0^1 d\lambda\, \iint d\1 d\2\, n_\lambda^{(2)}(\1,\2)w(\1,\2) \label{eqn:Henderson5-2-12}
\end{align}
The pair density itself can be expanded as
\begin{align}
  n_\lambda^{(2)}(\1,\2) &= n_0^{(2)}(\1,\2) + \lambda\frac{\partial n_\lambda^{(2)}(\1,\2)}{\partial\lambda}\bigg|_{\lambda = 0} + \mathcal{O}(\lambda^2)
\end{align}
Applying this to the \fixme{0th, 1st or 2nd, depending on how you think of it} term in equation~\ref{eqn:Henderson5-2-12}, we have
\begin{align}
  \frac{\beta F_1}{N} &= \frac{\beta}{2N}\iint d\1 d\2\, n_0^{(2)}(\1,\2)w(\1,\2) \\
  &= \frac{\beta n}{2}\int d\mathbf{r}_{12}\, g_0(\1,\2)w(\1,\2)
\end{align}
The second-order $\lambda$ term is quite a bit more complicated:
\begin{widetext}
 \begin{align}
   \begin{split}
   \frac{\beta F_2}{N} =&{} -\frac{\beta^2}{2}\left[ \frac{n}{2}\int d\2\, g_0(\1,\2)w^2(\1,\2) \right. \\ &{} + n^2 \iint d\2 d\3\, g_0^{(3)}(\1,\2,\3)w(\1,\2)w(\1,\3) \\ &{} \left. + \frac{n^3}{4}\iiint d\2 d\3 d\4\, \left( g_0^{(4)}(\1,\2,\3,\4) - g_0^{(2)}(\1,\2)g_0^{(2)}(\3,\4) \right)w(\1,\2)2(\3,\4) \right] \\ &{} - \frac{1}{4}S_0(0)\left[ \frac{\partial}{\partial n}\left( n^2\int d\2\, g_0(\1,\2)w(\1,\2) \right)^2 \right]
   \end{split}
 \end{align}
\end{widetext}
This term requires use to know the form of higher-order correlation functions and the structure function $S_0(k)$ of the reference system. These things are very difficult. Hence, we use approximations, as outlined in section~\ref{sub2sec:disp}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}\label{sec:methods}

@@

>>>>

% vector
\newcommand{\rr}{\ensuremath{\mathbf{r}}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\fixme{Write introduction; why do we do this? why is it useful? how is this relevant? what is the history?}

@@

Where $\fattr$ is the contribution due to the longest-wavelength
density fluctuations. At this stage, I do not entirely understand why
Forte splits up $\fattr$.

@@

\fixme{And introduction to TPT---why do we use it?}\davidsays{We use
  TPT because it gives a good description of simple liquids, as long
  as you are far from the critical point.  Thus it covers most of our
  bases.  It is also an elegant theory, since it comes from a rigorous
  power series expansion in a small parameter... or one that one hopes
  is small. }

This discussion follows primarily from \textit{Theory of Simple
  Liquids}, by Hansen and McDonald\cite{Hansen06}.

The pair potential $v(\1,\2)$ describes the interaction between two
hard spheres. For the square-well model, the pair potential is
\begin{align}
  v_\text{HS}(\1,\2) &=
    \begin{cases}
      \infty & r < \sigma \\
      0 & \sigma < r
    \end{cases}
\end{align}
\fixme{When $v_\lambda$ is derived below, the $w$
should be the attraction portion (i.e.~the $-\varepsilon$ between $\sigma$ and $\lambda\sigma$), and $v_{HS}$ should
just be the hard-sphere potential (without attraction).  That's how
the TPT works, it is the attraction that is being added in with the
$\lambda$ proportionality.}

Now, consider this to be the reference, and add a small perturbation:
\begin{align}
  v_\lambda(\1,\2) &= v_\text{HS}(\1,\2) + \lambda w(\1,\2) \label{eqn:small-perturbation}
\end{align}

The total potential energy of our system and its derivatives with resepect to $\lambda$---which become important later---are
\begin{align}
  V_N(\lambda) &= \sum_{i=1}^N\sum_{j>i}^N v_\lambda(\mathbf{r}_i,\mathbf{r}_j) \\ % \label{eq:VN} \\
  \hookrightarrow \frac{\partial V_N(\lambda)}{\partial\lambda} &= \sum_{i=1}^N\sum_{j>i}^N w(\mathbf{r}_i,\mathbf{r}_j) \nonumber \\
  &\equiv W_N \\
  \hookrightarrow \frac{\partial^2 V_N(\lambda)}{\partial\lambda^2} &= 0
\end{align}

The \emph{configuration integral} (the potential energy component of the partition function) and its derivative with respect to $\lambda$ are
\begin{align}
  Z_N(\lambda) &= \int d\rr^N\, e^{-\beta V_N(\lambda)} \\
  \hookrightarrow \frac{\partial Z_N(\lambda)}{\partial\lambda} &=  \int d\rr^N\, \frac{\partial}{\partial\lambda}e^{-\beta V_N(\lambda)} \\
  &= \int d\rr^N\, -\beta\frac{\partial V_N(\lambda)}{\partial\lambda}e^{-\beta V_N(\lambda)} \\
  &= \int d\rr^N\, -\beta W_N e^{-\beta V_N(\lambda)}
\end{align}
And the non-ideal part of the free energy (i.e.~the excess free energy) and its derivative are
\begin{align}
  F &= -\kT\ln\left( \frac{Z_N}{V^N} \right) \\
  \hookrightarrow \frac{\partial F}{\partial\lambda} &= \frac{V^N}{Z_N}\frac{\partial}{\partial\lambda}\left( \frac{Z_N}{V^N} \right) \\
  &= -\kT\left( \frac{1}{Z_N}\frac{\partial Z_N}{\partial\lambda} \right) \\
  &= \frac{1}{Z_N} \int d\rr^N\, W_N e^{-\beta V_N(\lambda)}\\
  &= \left\langle W_N \right\rangle_\lambda
\end{align}
(where $-\kT$ and $-\beta$ have divided out to $1$). Here, $V^N$ is
the total volume taken to the $N^{th}$ power, and
$\left\langle W_N \right\rangle_\lambda$ is the ensemble
average of $W_N$, with the subscript indicating some given
value of $\lambda$. We can simplify this even further by noting
\begin{align}
  \left\langle W_N \right\rangle &= \left\langle \sum_i\sum_jw(\mathbf{r}_i,\mathbf{r}_j) \right\rangle \\
  &= \frac{1}{2}N^2\left\langle w(\1,\2) \right\rangle
  \intertext{which gives us}
  \frac{\partial F}{\partial\lambda} &= \frac{1}{2}N^2\left\langle w(\1,\2) \right\rangle_\lambda
\end{align}

At this point, note that we have an exact equation with no approximation. Now take a series expansion:
\begin{align}\begin{split} % too long; use split environment, and align to a space (&{})
  \left\langle W_N(\lambda) \right\rangle_\lambda = &{} \left\langle W_N(\lambda)\right\rangle_{\lambda = 0} + (\lambda)\frac{\partial}{\partial\lambda}\left\langle W_N(\lambda) \right\rangle_{\lambda}\bigg|_{\lambda = 0} \\ &{} + \mathcal{O}(\lambda^2)
\end{split}\end{align}
The derivative term is
\begin{align}
  \frac{\partial}{\partial\lambda}\left\langle W_N(\lambda) \right\rangle_{\lambda} &= \left\langle V_N^{''} \right\rangle_\lambda - \beta\sigma_\lambda^2
\end{align}
where
\begin{align}
  \sigma_\lambda^2 &\equiv \left\langle \left[ W_N(\lambda) \right]^2 \right\rangle_\lambda - \left\langle W_N(\lambda) \right\rangle^2_\lambda
\end{align}
Now note that $W_N$ has no dependence on $\lambda$, therefore $W_N' = 0$, and
\begin{align}
  \frac{\partial}{\partial\lambda}\left\langle W_N(\lambda) \right\rangle_{\lambda} &= - \beta\sigma_\lambda^2 \\
  \therefore \left\langle W_N(\lambda) \right\rangle_\lambda &= \left\langle W_N(\lambda)\right\rangle_{\lambda = 0} - \lambda\beta\sigma_{\lambda=0}^2 + \mathcal{O}(\lambda^2)
\end{align}

\davidsays{The derivative is (pretty) easy if you write your ensemble
  average as a multidimensional integral, as in
  Eq.~\ref{eqn:dFdlambda}.  Write down $dF/d\lambda$ in terms of $Z_N$
  and an integral of Boltzmann factors times $W_N$.  Then when you
  take a derivative, it hits top and bottom, but each is an integral
  of an exponential, so those are easy to differentiate.  A little
  math will give you this variance formula.}

\fixme{Below this, I have not updated}

Putting this together, we have
\begin{align}
  \begin{split}
    \beta F = &{} \beta F_0 + \beta(1 - 0)\left\langle W_N(\lambda) \right\rangle_{\lambda = 0} \\ &{} - \beta\frac{1}{2}(1 - 0)^2\left(\left\langle W_N'(\lambda = 0) \right\rangle_{\lambda = 0} - \beta^2\sigma^2_{\lambda = 0} \right)
  \end{split} \\
  \begin{split}
    =&{}  \beta F_0 + \beta\left\langle W_N(\lambda) \right\rangle_{\lambda = 0} \\ &{} - \beta\frac{1}{2}\left(\left\langle W_N'(\lambda = 0) \right\rangle_{\lambda = 0} - \beta^2\sigma^2_{\lambda = 0} \right) \label{eqn:complicated-HTE}
  \end{split}
\end{align}
Now, we can define the total perturbation energy as
\begin{align}
  W_N &= \sum_{i=1}^N\sum_{j>i}^N w_\lambda(\mathbf{r}_i,\mathbf{r}_j)
\end{align}
Then, following from equation~\ref{eqn:small-perturbation},
\begin{align}
  W_N &= \frac{\partial}{\partial\lambda}\left(\sum_{i=1}^N\sum_{j>i}^N \lambda w(\mathbf{r}_i,\mathbf{r}_j)\right) \nonumber \\
  &= W_N \\
  \therefore W_N' &= 0
\end{align}
\davidsays{Ah ha! Here you do what I mentioned earlier.  I'd tend to
  put this earlier, so you can throw away the $V_N''$ term sooner.
  And also talking about $W_N$ with this definition I would find nicer
  and clearer than all the $V_N'$.}  With this in mind, we can
simplify equation~\ref{eqn:complicated-HTE} to the
\emph{high-temperature expansion}, first derived by
Zwanzig:\cite{Zwanzig54}
\begin{align}
  \begin{split}
    \beta F = &{} \beta F_0 + \beta\left\langle W_N \right\rangle_0  \\ &{} - \frac{1}{2}\beta^2\left( \left\langle W_N^2 \right\rangle_0 - \left\langle W_N \right\rangle_0^2 \right) + \mathcal{O}(\beta^3)
  \end{split}
\end{align}
Zwanzig further showed that the $n^{th}$ term could be written in terms of the mean fluctuations $\left\langle \left[ W_N - \left\langle W_N\right\rangle_0 \right]^\nu \right\rangle_0$ with $\nu \leq n$.

Writing the statistical averages in terms of the pair density
$n_\lambda^{(2)}(\1,\2)$ (i.e. the probability of having a sphere at
\1 and \2 \fixme{make this more clear?}\davidsays{I'd perhaps phrase
  it as ``probability per volume squared of having one sphere at \1
  and another at \2''}) gives us
\begin{align}
  \frac{\beta F}{N} &= \frac{\beta F_0}{N} + \frac{\beta}{2N}\int_0^1 d\lambda\, \iint d\1 d\2\, n_\lambda^{(2)}(\1,\2)w(\1,\2) \label{eqn:Henderson5-2-12}
\end{align}
\davidsays{Here's another place where all the $N$s on the bottom are
  muddying things up, I think.  (like the $\beta$s were before).  I
  also think this discussion is pretty redundant with parts of the
  previous derivation in terms of $V_N$.}  The pair density itself can
be expanded as
\begin{align}
  n_\lambda^{(2)}(\1,\2) &= n_0^{(2)}(\1,\2) + \lambda\frac{\partial n_\lambda^{(2)}(\1,\2)}{\partial\lambda}\bigg|_{\lambda = 0} + \mathcal{O}(\lambda^2)
\end{align}
Applying this to the \fixme{0th, 1st or 2nd, depending on how you
  think of it}\davidsays{it's ``second'' since ``terms'' are things
  that are added together, while factors are things that are
  multiplied together.  And in Eq~\ref{eqn:Henderson5-2-12} there are
  only two things added together.  (I figured this terminology out on
  my own some time after becoming a professor... it seems to be used,
  but not taught).} term in equation~\ref{eqn:Henderson5-2-12}, we
have
\begin{align}
  \frac{\beta F_1}{N} &= \frac{\beta}{2N}\iint d\1 d\2\, n_0^{(2)}(\1,\2)w(\1,\2) \\
  &= \frac{\beta n}{2}\int d\mathbf{r}_{12}\, g_0(\1,\2)w(\1,\2)
\end{align}
The second-order $\lambda$ term is quite a bit more complicated:
\begin{widetext}
 \begin{align}
   \begin{split}
   \frac{\beta F_2}{N} =&{} -\frac{\beta^2}{2}\left[ \frac{n}{2}\int d\2\, g_0(\1,\2)w^2(\1,\2) \right. \\ &{} + n^2 \iint d\2 d\3\, g_0^{(3)}(\1,\2,\3)w(\1,\2)w(\1,\3) \\ &{} \left. + \frac{n^3}{4}\iiint d\2 d\3 d\4\, \left( g_0^{(4)}(\1,\2,\3,\4) - g_0^{(2)}(\1,\2)g_0^{(2)}(\3,\4) \right)w(\1,\2)2(\3,\4) \right] \\ &{} - \frac{1}{4}S_0(0)\left[ \frac{\partial}{\partial n}\left( n^2\int d\2\, g_0(\1,\2)w(\1,\2) \right)^2 \right]
   \end{split}
 \end{align}
\end{widetext}
This term requires use to know the form of higher-order correlation functions and the structure function $S_0(k)$ of the reference system. These things are very difficult. Hence, we use approximations, as outlined in section~\ref{sub2sec:disp}.

\davidsays{ you can say something to the effect
  of ``in the next section we will see a simple approximation for this
  term.''  Hansen's explanation of TPT is not very clear, which makes
  it all the more valuable to make \emph{this} a clear and lucid
  explanation.  I'd love to see just a couple more steps at key
  places---largely where you were confused. This
  has been an excellent first shot, though! }

@@

\subsubsection{Ideal gas}\label{sub2sec:ID}
The ideal gas term is given as
\begin{align}
  \fid &= n\kT\left(\log(n) - 1\right)
\end{align}

\subsubsection{Hard sphere repulsion}\label{sub2sec:HS}
Hard sphere repulsive forces are dealt with by the White Bear version
of Fundamental-Mearuse Theory.\cite{Roth02} The hard sphere excess
free energy is given in the homogeneous case as
\begin{align}
  \fhs &= \kT\left( \Phi_1(n) + \Phi_2(n) + \Phi_3(n) \right)
\end{align}
The $\Phi_j(n)$ terms are given as
\begin{align}
  \Phi_1(n) &= -n_0(n)\ln(1 - n_3(n)) \\
  \Phi_2(n) &= \frac{n_1(n)n_2(n)}{1 - n_3(n)} \\
  \Phi_3(n) &= n_2^3(n)\left( \frac{n_3(n) + (1 - n_3(n))^2\ln(1 - n_3(n))}{36\pi n_3^2(n)(1 - n_3(n))^2} \right)
\end{align}
The \emph{fundamental measure densities} are
\begin{align}
  n_0(n) &= \frac{n_2}{4\pi R^2} \nonumber \\
  &= n \\
  n_1(n) &= \frac{n_2}{4\pi R} \nonumber \\
  &= nR \\
  n_2(n) &= n4\pi R^2 \\
  n_3(n) &= n\frac{4}{3}\pi R^3 \nonumber \\
  &= \eta
\end{align}
where $\eta$ is the packing fraction.

@@

We use the isothermal compressibility in terms of packing fraction
$\eta$, given by the Percus-Yevick exprssion:\cite{Barker76}
\begin{align}
  K^\text{HS} &= \frac{\left(1 - \eta\right)^4}{1 + 4\eta + 4\eta^2}
\end{align}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}\label{sec:methods}

@@

For this work, I use $\lambda_\text{SW} = 1.5$.
